Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-10 paper/structureScene.tex
write section VII

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usetikzlibrary{arrows.meta}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}
\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
\node (omlabel1) at (3.5, 1) {$t$};
\draw[-{Latex[length=2mm]}] (0, 1) -- (omlabel1);
\draw[-{Latex[length=2mm]}] (0, 1) -- (0, 2);
\node[anchor=south west,inner sep=0] at (0, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q8.png}};
\node at (2, -0.25) {(a)};
\node (omlabel2) at (8, 1) {$t$};
\draw[-{Latex[length=2mm]}] (4.5, 1) -- (omlabel2);
\draw[-{Latex[length=2mm]}] (4.5, 1) -- (4.5, 2);
\node[anchor=south west,inner sep=0] at (4.5, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q1.png}};
\node at (6.5, -0.25) {(b)};
\end{tikzpicture}
\caption{
\label{fig:gammatones}
Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$. Blue and red oscillations represent the real and imaginary parts. The orange envelope represents the complex modulus.}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}
\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
\node[anchor=south west,inner sep=0] at (-0.36, 0) {\includegraphics[height=2cm,width=5cm]{feature_histogram.png}};
\node (histlabel1) at (2.3, 0.01) {$\mathbf{S}\boldsymbol{x}(\gamma)$};
\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (histlabel1);
\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (-0.3, 2.5);
\node at (0.8, -0.35) {(a)};
\node (histlabel2) at (7.6, 0.01) {$\log \mathbf{S}\boldsymbol{x}(\gamma)$};
\node[anchor=south west,inner sep=0] at (3.45, 0) {\includegraphics[height=2cm,width=3cm]{feature_histogram_logcompressed.png}};
\draw[-{Latex[length=2mm]}] (3.2, 0.01) -- (histlabel2);
\draw[-{Latex[length=2mm]}] (4.9, 0.01) -- (4.9, 2.5);
\node at (4.9, -0.35) {(b)};
\end{tikzpicture}
\caption{
\label{fig:histograms}
Histogram of values taken by the first-order scattering coefficient $\mathbf{S}\boldsymbol{x}(\gamma)$, corresponding to a center acoustic frequency of $302\,\mathrm{Hz}$,
(a) before and (b) after logarithmic compression.}
\end{center}
\end{figure}

@@

\begin{itemize}
\item step 1: features extraction.
\item step 2: scene-wise clustering step. A clustering is performed on each scene using an enhanced version of the popular K-means algorithm known as K-means$++$ \cite{arthur2007k}, which differs from k-means method in terms of selection of starting points. Each scene is then describe with a set of centroids.
\item step 3: Centroids similarity. The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}: \\
\begin{equation}
\begin{split}
K^c_{ij} & =exp\left( - \dfrac{\parallel c_i - c_j \parallel^2}{\sigma_{i}\sigma_{j}} \right) \\
\sigma_{i} & =\parallel c_i - c_N \parallel
\end{split}
\end{equation}

@@

\section{Experimental Evaluation}

@@

The object-based approach is assessed considering both an ASS and an ASC scenario:

\begin{itemize}
\item \emph{ASS}: It is an unsupervised scenario. Evaluation is performed on the private dataset of the DCASE 2013 challenge, using the precision at rank $k$ ($k=[1,\ldots,9]$) metrics. Note that a $p@1$ is equivalent to an accuracy computed based on the labels of the 1st nearest neighbors of the points to classify.

\item \emph{ASC}: It is a supervised scenario. The systems are evaluated  with five-fold  stratified cross validation on the  private dataset of the DCASE 2013 challenge. The folds are identical to those used in the original challenge. A linear Support Vector Machine (SVM) is used as classifier. For object-based approach, we only consider the step 2. Consequently, each scene is represented by a set of centroids and each centroid is classified separately. The final scene classification is based on a majority vote. In this case, the object-based approach may be seen as a mid integration strategy.
\end{itemize}

@@

ASC, ASS:   Similarity between scenes features is then computed using a Gaussian kernel with local scaling.

The object-based approach is compared to standard approaches using early integration strategy for the ASS scenario, and both early and late integration strategies for the ASC scenario (see Section \ref{XX}).

@@

Two types features are used to describe the scenes:

\begin{itemize}
\item \emph{temporal-scattering}: Each scene is described by 128 vectors of scattering coefficients. 
\item \emph{Mel Frequency Cesptral Coefficients} (MFCCs): Different set of parameters were tested to compute the MFFCs, we here present only the results for the best setting, which is similar to the one used by the winners of the previous DCASE 2013 challenge \cite{roma2013}. We use 40 MFCCs (including the 0 energy coefficient) computed for windows of 50ms and hops of 25ms, with a limited frequency range going from $27.5$Hz to $1000$Hz. This setting gives us 600 feature vectors per scenes. To reduce the data dimensionality, a pooling step is performed on the MFCCs vectors: each set of MFCCs vectors is dividing into $n$ non-overlapping $t$-seconds long slices. Each $n$ MFCC slices is then averaged over time. As the object-based approach (see \ref{XX}) involves a clustering step, we want to ensure that each scene is described by circa the same number of vectors prior to the clustering, for both the temporal-scattering and the MFCCs. To do so, $t$ is set to 250ms, which gives us 120 MFCCs vectors per scenes. 
\end{itemize}

For the ASC scenario, the features are standardized prior to the SVM classification step.

@@

\section{Results: Acoustic Scene Classification}
Support vector machines are large-margin binary discriminators with tunable regularization of misclassified examples.

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
%\usepackage{tikz}
%\usetikzlibrary{arrows,positioning}
%\usetikzlibrary{arrows.meta}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

@@

%\begin{figure}
%\begin{center}
%\begin{tikzpicture}
%\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
%\node (omlabel1) at (3.5, 1) {$t$};
%\draw[-{Latex[length=2mm]}] (0, 1) -- (omlabel1);
%\draw[-{Latex[length=2mm]}] (0, 1) -- (0, 2);
%\node[anchor=south west,inner sep=0] at (0, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q8.png}};
%\node at (2, -0.25) {(a)};
%\node (omlabel2) at (8, 1) {$t$};
%\draw[-{Latex[length=2mm]}] (4.5, 1) -- (omlabel2);
%\draw[-{Latex[length=2mm]}] (4.5, 1) -- (4.5, 2);
%\node[anchor=south west,inner sep=0] at (4.5, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q1.png}};
%\node at (6.5, -0.25) {(b)};
%\end{tikzpicture}
%\caption{
%\label{fig:gammatones}
%Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$. Blue and red oscillations represent the real and imaginary parts. The orange envelope represents the complex modulus.}
%\end{center}
%\end{figure}

@@

%\begin{figure}
%\begin{center}
%\begin{tikzpicture}
%\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
%\node[anchor=south west,inner sep=0] at (-0.36, 0) {\includegraphics[height=2cm,width=5cm]{feature_histogram.png}};
%\node (histlabel1) at (2.3, 0.01) {$\mathbf{S}\boldsymbol{x}(\gamma)$};
%\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (histlabel1);
%\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (-0.3, 2.5);
%\node at (0.8, -0.35) {(a)};
%\node (histlabel2) at (7.6, 0.01) {$\log \mathbf{S}\boldsymbol{x}(\gamma)$};
%\node[anchor=south west,inner sep=0] at (3.45, 0) {\includegraphics[height=2cm,width=3cm]{feature_histogram_logcompressed.png}};
%\draw[-{Latex[length=2mm]}] (3.2, 0.01) -- (histlabel2);
%\draw[-{Latex[length=2mm]}] (4.9, 0.01) -- (4.9, 2.5);
%\node at (4.9, -0.35) {(b)};
%\end{tikzpicture}
%\caption{
%\label{fig:histograms}
%Histogram of values taken by the first-order scattering coefficient $\mathbf{S}\boldsymbol{x}(\gamma)$, corresponding to a center acoustic frequency of $302\,\mathrm{Hz}$,
%(a) before and (b) after logarithmic compression.}
%\end{center}
%\end{figure}

@@

\begin{itemize}
\item step 1: features extraction.
\item step 2: scene-wise clustering step. A clustering is performed on each scene using an enhanced version of the popular K-means algorithm known as K-means$++$ \cite{arthur2007k}, which differs from k-means method in terms of selection of starting points. Each scene is then describe with a set of centroids.
\item step 3: Centroids similarity. The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}: \\
\begin{equation}
\label{eq:kc}
\begin{split}
K^c_{ij} & =exp\left( - \dfrac{\parallel c_i - c_j \parallel^2}{\sigma_{i}\sigma_{j}} \right) \\
\sigma_{i} & =\parallel c_i - c_N \parallel
\end{split}
\end{equation}

@@

\section{Experimental Evaluation}
\label{sec:ExpEval}

@@

The influence of the temporal-scattering transform and the object-based approach (\emph{ob}) are assessed in an unsupervised setting (\emph{i.e.} ASS) and in a supervised setting (\emph{i.e.} ASC).

For the ASS setting, evaluation is performed on the private dataset of the DCASE 2013 challenge. The metric used is the precision at rank $k$ ($p@k$), which is the  average  number  of  items  of  the  same  class among the $k$ closest items averaged for all possible seed items. The $p@k$ is computed for $k=[1,\ldots,9]$. Note that a $p@1$ is equivalent to an accuracy computed based on the labels of the 1st nearest neighbors of the items to classify.

For the ASC setting, the systems are evaluated  with five-fold  stratified cross validation on the private dataset of the DCASE 2013 challenge. The folds are identical to those used in the original challenge. Optimal parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approach and the scaling parameters $N$ of the RBF kernels (see Eq. \ref{eq:kc}), are learned on the public dataset of the DCASE 2013 challenge, using five-fold  stratified cross validation as well.

@@

The \emph{ob} approach is compared to commonly used approaches using an early integration strategy (\emph{ei}) for the ASS setting, and both an early and a late integration (\emph{li}) strategy for the ASC setting (see Section \ref{XX}).

@@

Experiments are carried out using temporal-scattering coefficients as well as Mel Frequency Cesptral Coefficients (MFCCs) as features. For the temporal-scattering, each scene is described by 128 vectors of scattering coefficients \gl{vincent: windows and hops ?}. Different sets of parameters were tested to compute the MFFCs. We here report only the results for the best setting, which is similar to the one used by the winners of the previous DCASE 2013 challenge \cite{roma2013}. 40 MFCCs (including the first energy coefficient) are computed for windows of 50ms and hops of 25ms, with a limited frequency range going from $27.5$Hz to $1000$Hz. This setting gives us 600 feature vectors per scenes. It has been reported that classifying the full set of frames directly may not be the best approach. In order to reduce the data dimensionality, a pooling step is performed on the MFCCs vectors: each set of MFCCs vectors is dividing into $n$ non-overlapping $t$-seconds long slices. Each $n$ MFCC slices is then averaged over time. As the \emph{ob} approach involves a clustering step, it is desirable to ensure that each scene is described by circa the same number of vectors,for both the temporal-scattering and the MFCCs, prior to running the clustering. Thus, $t$ is set to 250ms, which gives us 120 MFCCs vectors per scenes.

\subsection{Classifier}

As most of the 2013 DCASE challenge participant did, a Support Vector Machine (SVM), which is a large-margin binary discriminators with tunable regularization of misclassified examples, is used as classifier for the ASC setting. For the \emph{ob} approach, we use XX. For both the \emph{ei} and \emph{li} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approach, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All features, that is the frames, the pooled frames or the centroids depending on the approach considered, are standardized prior to be filled into the classifier. The standardization is computed with respect to the train/test set split of the cross validation scheme (see \ref{}).

@@

\section{Results: Acoustic Scene Classification}
